---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nottshcFFT

<!-- badges: start -->
<!-- badges: end -->

The aim of this package is to collect together the functions used in the Friends and Family (FFT) monthly return which requires a data download from a clinical system which is then uploaded to the MySQL Patient Feedback database.

The upload from a clinical system includes Comments which can be cleaned, to some extent, before loading. Once in the MySQL database they are further checked for identifiable information and safeguarding by staff in the Patient Involvement team.

This package also serves as a public example of packages created and used by the CDU Data Science Team.

## Installation

You can install the development version of nottshcFFT from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Lextuga007/nottshcFFT")
```

**You might get an error/warning/not load if you are on the VPN!**

It is preferable to build from the repository rather than locally as
this should be what everyone in the team has access to. To build and
test any new functions use `Ctrl+Shift+L` to load locally for the
session.

However, the person who is maintaining the package may want to install from
the remote development using code:

``` r
# install.packages("remotes")
remotes::install_github("CDU-data-science-team/nottshcFFT@development")
```

## Loading the package

```{r example}
library(nottshcFFT)
```

